Computing Entropies With Nested Sampling

### 2017-08-11 paper/response.tex

Imagine doing simple Monte Carlo to get $Z$, by drawing from the prior and
collecting likelihood values, which you'll want to average. A histogram of
those likelihood values will look ridiculous, and you might have to wait
a million years until you get enough points such that your average becomes
accurate, because it will be dominated by huge likelihoods which are seen
rarely. Most NS people talk about this in terms of the parameter space, but
it also has an interpretation in terms of a `probability distribution for
$L$' which is implied by $\pi$.

{\quote
6. Just before (14) and in (15): I do not understand the notation regarding the implicit likelihood boundary involving \\mathbb\{1\}}

I've added a bit of explanation of the indicator function notation.

{\quote
7. After (26) what is meant by "NS repetitions"?}

It's the number of reference particles
whose depth was estimated using an NS run. I've added a sentence to this effect.

{\quote
8. After (51): I do not understand the statement "The variance of this mutual information estimate was reduced by using a common sequence of reference points for the marginal and joint entropy runs, an instance of the ‘common random numbers’ technique 1"}

@@

9. It wasn't clear to me how the distance function (25) was chosen and why.

10. I had some questions about how the algorithm was conceived.  I had a difficult time envisioning how the blue distribution played the role of the prior, and why.  Perhaps some explanation is necessary here since NS is usually presented to as to assume that parameter changes were implemented to maintain a uniform prior.

11.  It was not entirely clear to me how the algorithm was used to estimate the entropy of a Gaussian.  How was the posterior (24) arrived at.  The prior is normal.  But what about the likelihood?  And then how was the distance measure (25) computed?

{\quote
There are a number of typos:

1. End of Section 1: "I sometimes write general formulae are written ..."}
Fixed.

{\quote
2. Missing citation in first sentence of Section 6}
I removed that citation.

{\quote
3. After (47): question mark missing in case ii)}
Fixed.

### 2017-08-11 paper/ms.tex
More work on Kevin's comments

I ran the algorithm and computed the average depth using a tolerance of
$r=10^{-3}\sqrt{100}$, so that the RMS difference between
points in the two datasets was about $10^{-3}$.
From the algorithm, the estimate of the expected depth was
\begin{align}
\left<\depth_{\boldsymbol{x}}\right> &= 698.25 \pm 0.34.
\end{align}
The uncertainty here is the standard error of the mean, i.e., the
standard deviation of the depth estimates divided by square root of
the number of NS repetitions.

@@

Consider $n=100$ data values, partitioned into two halves, so
$\boldsymbol{y} = \{x_1, ..., x_{50}\} = \{y_1, ..., y_{50}\}$
is the first half of the data and
$\boldsymbol{z} = \{x_{51}, ..., x_{100}\} = \{z_1, ..., z_{50}\}$
is the second half. Let $\ytot$ and $\ztot$ be the totals of the two
subsets of the data:
\begin{align}
\ytot &= \sum_{i=1}^{50} y_i \\
\ztot &= \sum_{i=1}^{50} z_i.
\end{align}
In this section I use the algorithm to answer the questions:
i) How uncertain is $\ytot$?; ii) How uncertain is $\ztot$; and
iii) How informative is $\ytot$ about $\ztot$? These are quantified by
$H(\ytot)$, $H(\ztot)$, and $I(\ytot; \ztot)$ respectively. This can
be done despite the fact that $\alpha$ is unknown.

>>>>

I ran the algorithm and computed the average depth using a tolerance of
$r=10^{-3}\sqrt{100}$, so that the RMS difference between
points in the two datasets was about $10^{-3}$.
From the algorithm, the estimate of the expected depth was
\begin{align}
\left<\depth_{\boldsymbol{x}}\right> &= 698.25 \pm 0.34.
\end{align}
The uncertainty here is the standard error of the mean, i.e., the
standard deviation of the depth estimates divided by square root of
the number of NS repetitions {\revision (the number of reference particles
whose depth was evaluated)}.

@@

Consider $n=100$ data values, partitioned into two halves, so
$\boldsymbol{y} = \{x_1, ..., x_{50}\} = \{y_1, ..., y_{50}\}$
is the first half of the data and
$\boldsymbol{z} = \{x_{51}, ..., x_{100}\} = \{z_1, ..., z_{50}\}$
is the second half. Let $\ytot$ and $\ztot$ be the totals of the two
subsets of the data:
\begin{align}
\ytot &= \sum_{i=1}^{50} y_i \\
\ztot &= \sum_{i=1}^{50} z_i.
\end{align}
In this section I use the algorithm to answer the questions:
i) How uncertain is $\ytot$?; ii) How uncertain is $\ztot$?; and
iii) How informative is $\ytot$ about $\ztot$? These are quantified by
$H(\ytot)$, $H(\ztot)$, and $I(\ytot; \ztot)$ respectively. This can
be done despite the fact that $\alpha$ is unknown.
